---
title: "hw02-Daniel-Kang.Rmd"
author: "Daniel Kang"
date: "9/29/2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# download csv file to your working directory
# (do NOT include this code in your Rmd)
github <- "https://github.com/ucb-stat133/stat133-fall-2017/raw/master/"
file <- "data/nba2017-player-statistics.csv"
csv <- paste0(github, file)
download.file(url = csv, destfile = 'nba2017-player-statistics.csv')
getwd()
library(dplyr)
```

#basis#2
```{r}
#the columns Player, Team, and Experience have to be declared as type character.
getwd()
cat1 <- read.csv("nba2017-player-statistics.csv", TRUE, ",")
cat1s <- read.csv("nba2017-player-statistics.csv", TRUE, colClasses = c("character","character","factor", "character", "double", "integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer","integer" ))
str(cat1)
```

#readr#2
```{r}
library(readr)
cat2 <- read_csv("data/nba2017-player-statistics.csv")
str(cat2)

cat2 <- read_csv("nba2017-player-statistics.csv", 
                 col_types = list(Player = col_character(), 
                 Team = col_character(), 
                 Position = col_factor(c("C", "SF", "PF", "PG","SG")),
                 Experience = col_character(), 
                 Salary = col_double())
                 
)
str(cat1)

```

#3 change the values in Ecperience
```{r}

cat1$Experience[cat1$Experience == 'R'] <- 0
cat1$Experience = as.integer(cat1$Experience)

```

#4 Performance of players
```{r}

missed_fg <- cat1$FGA - cat1$FGM
missed_ft <- cat1$FTA - cat1$FTM
PTS <- cat1$Points2 * 2 + cat1$Points3*3 + cat1$FTM
AST <- cat1$AST
STL <- cat1$STL
TO <- cat1$TO
REB <- cat1$OREB+cat1$DREB
GP <- cat1$GP
BLK <- cat1$BLK
EFF <- (PTS + REB + cat1$AST + cat1$STL + cat1$BLK - missed_fg - missed_ft - cat1$TO)/GP
MPG <- cat1$MIN/cat1$GP
summary(EFF)

#graph
hist(EFF, breaks = 5,
     freq = TRUE,
     border = TRUE,
     xlim = c(-5,35),
     main = "Histogram of Effucuency (EFF)")
```

```{r}
#Disply the player, name, team, salary and EFF value of the top 10 players by EEF in decreasing order
cat1 <- mutate(cat1,EFF)
top10EFF <- arrange(cat1, desc(EFF))
top10EFF[1:10, c("Player", "Team", "Salary", "EFF")]
```

```{r}
#procide the names fo the players that have a negitive EFF
nEFF <- data.frame(cat1[EFF < 0,])
nEFF
```

```{r}
#Correlation
Correlation <- data.frame (
                          PTS = cor(EFF,PTS), 
                          REB = cor(EFF, REB),
                          AST = cor(EFF, AST), 
                          STL = cor(EFF, STL), 
                          BLK = cor(EFF, BLK),
                          TO = cor(EFF, (-1)* TO),
                          missed_fg = cor(EFF, (-1)*missed_fg), 
                          missed_ft = cor(EFF, (-1)*missed_ft)
                          
)
Correlation
```
```{r}
cat1 <- mutate(cat1,EFF)
str(cat1)
```
```{r}
#display
new_Cor <- sort(Correlation, decreasing = TRUE)
barplot(as.numeric(new_Cor), ylim = c(-1,1), main = 'Correlation between Player Stats and EFF', names.arg = variable.names(new_Cor), col = ifelse(as.numeric(new_Cor) > 0, "grey", "coral2"), border = NA)
abline(h = 0)
```
#5 Efficiency and Salary
```{r}
#5
X = data.frame(cat1$EFF, cat1$Salary)
plot(X, main = "Efficiency and Salary", xlab = "Efficiency", ylab = "Salary")
lines(lowess(X), col = "black", lwd = 2.5)
cor(cat1$EFF, cat1$Salary)
cat1[MPG >= 20, ]

```

```{r}
#creat players2
players2 <- data.frame(cat1[MPG >= 20, ] )
plot(players2$EFF,players2$Salary, ylab = "Salary", xlab = "Efficiency", cex = 0.7, col = "grey", main = "scatterplot between Efficiency and Salary ", lines(lowess(players2$EFF,players2$Salary), lwd = 2.5, col = "red"))
cor(players2$EFF, players2$Salary)


```
#6 Questions answer.
• What things were hard, even though you saw them in class/lab?
setting up the variable is hard for me.

• What was easy(-ish) even though we haven’t done it in class/lab?
assigning the variables.

• Did you need help to complete the assignment? If so, what kind of help?
yes I do. I need someone to explain how to use that function.

• How much time did it take to complete this HW?
more than 6 hours

• What was the most time consuming part?
First you need to have the right function to have the right variable and so you can have the tight graph. It take a lot of time to go back to find the mistake.

• Was there anything that you did not understand? or fully grasped?
the meaning of data frame is still a but confuse although i know how to use it.

• Was there anything frustrating in particular?
Not really.

• Was there anything exciting? Something that you feel proud of? (Don’t be shy, we
won’t tell anyone).
yes, due to I am a NBA fan so i have a lot of fun watching or testing the things that i made. I can put in some of my fav player stuff like that! thats so fun!

























